Summary Tables

### 2022-10-17 summary_tables.Rmd
Get NSCEN from io object

```{r load_objects = "asis", echo = F, message = F}
io <- readRDS("results/multi_city/io.rds")
# Assumes that multi_city_script.R has been run till 
# Get names of cities from the io object
cities <- names(io)[!names(io) %in% 'scen_prop']
LATAM <- TRUE
NSCEN <- 4
#cities <- c('accra','sao_paulo','buenos_aires')

@@

dat[[city]] <- io[[city]]$trip_scen_sets %>% 
  mutate(scenario = case_when(
    # scenario == "Scenario 1" ~ "PED_SC", 
    # scenario == "Scenario 2" ~ "CYC_SC",
    # scenario == "Scenario 3" ~ "CAR_SC",
    # scenario == "Scenario 4" ~ "MOT_SC",
    # scenario == "Scenario 5" ~ "BUS_SC",
    scenario == "Scenario 1" ~ "CYC_SC", 
    scenario == "Scenario 2" ~ "CAR_SC",
    scenario == "Scenario 3" ~ "BUS_SC",
    scenario == "Scenario 4" ~ "MOT_SC",
    scenario == "Baseline" ~ "Baseline")) %>% 
  group_by(scenario, trip_mode, trip_distance_cat) %>% 
  summarise(n = dplyr::n(), dist = sum(trip_distance, na.rm = T)) %>% 
  mutate(city = city)

>>>>

```{r load_objects = "asis", echo = F, message = F}
io <- readRDS("results/multi_city/io.rds")
# Assumes that multi_city_script.R has been run till 
# Get names of cities from the io object
cities <- names(io)[!names(io) %in% 'scen_prop']
LATAM <- F
AFRICA_INDIA = T
NSCEN <- nrow(io$scen_prop)
#cities <- c('accra','sao_paulo','buenos_aires')

@@

dat[[city]] <- io[[city]]$trip_scen_sets %>% 
  mutate(scenario = case_when(
    scenario == "Scenario 1" ~ "CYC_SC", 
    scenario == "Scenario 2" ~ "CAR_SC",
    scenario == "Scenario 3" ~ "BUS_SC",
    scenario == "Scenario 4" ~ "MOT_SC",
    scenario == "Baseline" ~ "Baseline")) %>% 
  group_by(scenario, trip_mode, trip_distance_cat) %>% 
  summarise(n = dplyr::n(), dist = sum(trip_distance, na.rm = T)) %>% 
  mutate(city = city)
